Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-12-21 paper.tex
Correct and expand discussion of Figs. 12-16 for compute-eta data

When we turn on scattering, the disk is no longer transparent to $\nu_x$,
and $\nu_x$ luminosities present the same qualitative $\theta$-dependence
as that of the other species.
In general, scattering increases luminosities for polar observers
($\theta \sim 0^\circ$) because additional high energy neutrinos
from the hypermassive neutron star are scattered by the disk back up to
the observer.
For observers in the equatorial plane ($\theta \sim 90^\circ$)
the effect of scattering is a decrease in energy luminosities,
since some of the highest energy neutrinos from deep in the interior
are scattered away from the line of sight by the disk.

@@

In Figs.~\ref{fig:nsns_cosA_distrib_G_00deg}
and \ref{fig:nsns_cosA_distrib_G_90deg}, we show the distributions of neutrino
number density over incoming angle
for the observer on the polar axis $\theta=0^\circ$,
and in the equatorial plane $\theta=90^\circ$,
defined analagously to Eqn.~\ref{eqn:J_per_cosA}.
As in the case of the collapse profile in Sec.~\ref{ssec:test_collapse},
the dominant effect of \emph{scat} on $\tilde{G}(\cos A)$
is to spread the distribution out to larger angles, by generally decreasing
the number of neutrinos coming from the core while increasing the number
of neutrinos coming from the disk.
\footnote{TODO: also examine spectra or average energies}

>>>>

When we turn on scattering, the disk is no longer transparent to $\nu_x$,
and $\nu_x$ luminosities present the same qualitative $\theta$-dependence
as that of the other species.
In general, scattering increases luminosities for polar observers
\footnote{TODO: in compute-eta data not true anymore for $\nu_e$}
($\theta \sim 0^\circ$) because additional high energy neutrinos
from the hypermassive neutron star are scattered by the disk back up to
the observer.
For observers in the equatorial plane ($\theta \sim 90^\circ$)
the effect of scattering is a decrease in energy luminosities,
since some of the highest energy neutrinos from deep in the interior
are scattered away from the line of sight by the disk.

@@

In Figs.~\ref{fig:nsns_cosA_distrib_G_00deg}
and \ref{fig:nsns_cosA_distrib_G_90deg}, we show the distributions of neutrino
number density over incoming angle
for the observer on the polar axis $\theta=0^\circ$,
and in the equatorial plane $\theta=90^\circ$,
defined analagously to Eqn.~\ref{eqn:J_per_cosA}.
As in the case of the collapse profile in Sec.~\ref{ssec:test_collapse},
the dominant effect of elastic scattering on $\tilde{G}(\cos A)$
is to spread the distribution out to larger angles, by generally decreasing
the number of neutrinos coming from the core while increasing the number
of neutrinos coming from the disk.
\footnote{TODO: with compute-eta data also explain why $G_{\nu_e}>G_{\bar{\nu}_e}$
  for $\theta=0$ at $\cos A>0.995$.}

For the observer in the equatorial plane,
Fig.~\ref{fig:nsns_cosA_distrib_G_90deg}, the disk is so optically thick to
$\nu_e$ that there is very little difference between \emph{scat} and
\emph{noscat} treatments for incoming angles $\cos A \lesssim 0.95$
corresponding to the volume inside of $r \lesssim 80$~km.
Also the stepped temperature gradient in the disk's spiral arms visible in
Figs.~\ref{fig:nsns_temp_merid} and \ref{fig:nsns_temp_equat} presents as a
stepped heavy-lepton neutrino number density distribution in
Fig.~\ref{fig:nsns_cosA_distrib_G_90deg} in the \emph{noscat} treatment,
since the pair production rate due to $e^{-}e^{+}$ annihilation,
producing $\nu_x$, is especially sensitive to temperature, going as
$T^9$ \cite[Sec.~7]{burr2006-neutrino_opacities}.
This stepped distribution is not visible in $\nu_e$ and $\bar{\nu}_e$ emission,
since we ignore pair processes for these species due to the dominance of
absorption and emission processes, obeying a shallower temperature-dependence;
nor is it visible in the \emph{scat} treatment of $\nu_x$, since scattering
tends to smear the incoming angle of the emission;
nor is it visible for any species or treatment in
Fig.~\ref{fig:nsns_cosA_distrib_G_00deg}, since the integration over the
azimuthal angle $B$ averages out any spiral structure for the observer
on the polar axis.
